method

### 2021-10-05 06_Paper/ER-ED/intro.Rmd

In the original study by Westbrook et al. [-@Westbrook2013], cognitive load was varied using the *N*-back task. 
Participants had to decide whether repeating a higher *N*-back level for larger, fixed monetary reward, or a lower level for a smaller, varying reward. 
In the current study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: we have to change the assumption that the easiest *N*-back level has the highest SV.
That is necessary, because there is nothing like an objectively easier and less effortful strategy.
As we have shown in previous studies, there are inter-individual differences in the preference of ER strategies [Scheffel2021].

>>>>

In the original study by Westbrook et al. [-@Westbrook2013], cognitive load was varied using the *N*-back task. 
Participants had to decide whether repeating a higher *N*-back level for larger, fixed monetary reward, or a lower level for a smaller, varying reward. 
In the current study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: we have to adapt the assumption that the easiest *N*-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies [@Scheffel2021].

### 2021-10-05 06_Paper/ER-ED/method.Rmd

_Part two: ER effort discounting._ <br>
In the second part, ER effort discounting took place.
The procedure of the discounting followed the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with an addition to be useful for the current study.
We used an adaption that allowed the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one.
For each possible pairing (distraction vs. distancing, distraction vs. suppression, and distancing vs. suppression), two strategies  with monetary values were presented.
The order of the comparisons was randomized.
Because there is no strategy that is objectively more difficult, all comparisons began with 
Participants were instructed to decide as realistically as possible, imaging the displayed money would really be up for election.

_Part three: ER choice._ <br>
After the discounting part, participants could choose which of the three ER strategies (distraction, distancing or suppression) they wanted to reapply.
Importantly, there were no further instruction, on what basis they should make their decision.

@@

>>>>

_Part two: ER effort discounting._ <br>
In the second part, ER effort discounting took place.
The procedure of the discounting followed the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with an addition to be useful for the current study.
We used an adaption that allowed the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one.

[...]
For each possible pairing (distraction vs. distancing, distraction vs. suppression, and distancing vs. suppression), two strategies  with monetary values were presented.
The order of the comparisons was randomized.
Because there is no strategy that is objectively more difficult, all comparisons began with 
Participants were instructed to decide as realistically as possible, imaging the displayed money would really be up for election.

_Part three: ER choice._ <br>
After the discounting part, participants chose which of the three ER strategies (distraction, distancing or suppression) they wanted to reapply.
Importantly, there were no further instruction, on what basis they should make their decision.

@@

[...]
